### 2014-04-22 docs/paper/paper.tex
resource utilization

A hardware implementation of the \design{} design was produced on a Xilinx VC707 development board, which includes a modern field-programmable gate array (FPGA)
device (Xilinx XC7VX485T-2FFG1761C). This device was chosen because of its ready availability on a development platform and its large logic capacity and available resources.
In particular, it provides 37080~Kb of on-chip block RAM and 2800 customizable DSP slices, both of which the Nengo-RT design requires in abundance in order to support
the largest possible implementation size.

% FIXME implemented design size

>>>>

A hardware implementation of the \design{} design was produced on a Xilinx VC707 development board, which includes a modern field-programmable gate array (FPGA)
device (Xilinx XC7VX485T-2FFG1761C). This device was chosen because of its ready availability on a development platform and its large logic capacity and available resources.
In particular, it provides 37080~Kb of on-chip block RAM and 2800 customizable DSP slices, both of which the Nengo-RT design requires in abundance.
Table~\ref{tbl:utilization} outlines the resource utilization of the implemented design.

\begin{table}
\begin{tabular}{|r|c|c|l|}
\hline
Resource & Used & Total & \% Used \\
\hline
\hline
Registers & 82~149 & 607~200 & 13\% \\
Lookup Tables & 101~859 & 303~600 & 33\% \\
Logic Slices & 43~596 & 75~900 & 57\% \\
Block RAM (18~Kb) & 914 & 2060 & 44\% \\
DSP & 1722 & 2800 & 61\% \\
\hline
\end{tabular}
\caption[\design{} resource utilization on VC707 development board.]
{Resource utilization of the \design{} design with 7 one-dimensional and 7 two-dimensional population units, and one decoded value buffer reserved for external inputs.
Resource totals are for the Xilinx XC7VX485T device.}
\label{tbl:utilization}
\end{table}
